---
title: "Fastball Analysis"
author: "Riley Feltner"
date: "2022-11-12"
output: html_document
---

#download data
```{r}
RightFB <- read.csv("Right FB.csv")
LeftFB <- read.csv("Left FB.csv")
RightSI <- read.csv("Right SI.csv")
LeftSI <- read.csv("Left SI.csv")
RightCT <- read.csv("Right CT.csv")
LeftCT <- read.csv("Left CT.csv")
```

#Summary Stats Right FB
```{r}
#install.packages("stargazer")
library(stargazer)
library(dplyr)


RightFB <- RightFB[c(2:4, 9, 11, 13, 18, 19)]

RightFB$ExAVG <- as.numeric(as.character(RightFB$ExAVG))
RightFB$ExSLG <- as.numeric(as.character(RightFB$ExSLG))
RightFB$Miss. <- as.numeric(as.character(RightFB$Miss.))
RightFB$K. <- as.numeric(as.character(RightFB$K.))
RightFB$Vel <- as.numeric(as.character(RightFB$Vel))
RightFB$TMIndVertBrk <- as.numeric(as.character(RightFB$TMIndVertBrk))

RightFB <- na.omit(RightFB)


RightFB1 <- filter(RightFB, P > 24)


RightFB1 %>%
  stargazer(type = "text",
            summary.stat = c("N", "median", "mean", "min", "max", "p25", "p75"),
            title = "Right Handed Pitcher's FB (>= 25 Pitches)")
```

#Summary Stats Left FB
```{r}

LeftFB <- LeftFB[c(2:6, 9, 11, 13, 18, 19)]

LeftFB$ExAVG <- as.numeric(as.character(LeftFB$ExAVG))
LeftFB$ExSLG <- as.numeric(as.character(LeftFB$ExSLG))
LeftFB$Miss. <- as.numeric(as.character(LeftFB$Miss.))
LeftFB$K. <- as.numeric(as.character(LeftFB$K.))
LeftFB$Vel <- as.numeric(as.character(LeftFB$Vel))
LeftFB$TMIndVertBrk <- as.numeric(as.character(LeftFB$TMIndVertBrk))

LeftFB <- na.omit(LeftFB)

LeftFB1 <- filter(LeftFB, P > 24)


LeftFB1 %>%
  stargazer(type = "text",
            summary.stat = c("N", "median", "mean", "min", "max", "p25", "p75"),
            title = "Left Handed Pitcher's FB (>= 25 Pitches)")
```

#Summary Stats Right SI
```{r}
RightSI <- RightSI[c(2:6, 9, 11, 13, 18, 19)]

RightSI$ExAVG <- as.numeric(as.character(RightSI$ExAVG))
RightSI$ExSLG <- as.numeric(as.character(RightSI$ExSLG))
RightSI$Miss. <- as.numeric(as.character(RightSI$Miss.))
RightSI$K. <- as.numeric(as.character(RightSI$K.))
RightSI$Vel <- as.numeric(as.character(RightSI$Vel))
RightSI$TMIndVertBrk <- as.numeric(as.character(RightSI$TMIndVertBrk))

RightSI <- na.omit(RightSI)

RightSI1 <- filter(RightSI, P > 24)


RightSI1 %>%
  stargazer(type = "text",
            summary.stat = c("N", "median", "mean", "min", "max", "p25", "p75"),
            title = "Right Handed Pitcher's SI (>= 100 Pitches)")
```

#Summary Stats Left SI
```{r}
LeftSI <- LeftSI[c(2:6, 9, 11, 13, 18, 19)]

LeftSI$ExAVG <- as.numeric(as.character(LeftSI$ExAVG))
LeftSI$ExSLG <- as.numeric(as.character(LeftSI$ExSLG))
LeftSI$Miss. <- as.numeric(as.character(LeftSI$Miss.))
LeftSI$K. <- as.numeric(as.character(LeftSI$K.))
LeftSI$Vel <- as.numeric(as.character(LeftSI$Vel))
LeftSI$TMIndVertBrk <- as.numeric(as.character(LeftSI$TMIndVertBrk))

LeftSI <- na.omit(LeftSI)

LeftSI1 <- filter(LeftSI, P > 24)


LeftSI1 %>%
  stargazer(type = "text",
            summary.stat = c("N", "median", "mean", "min", "max", "p25", "p75"),
            title = "Left Handed Pitcher's SI (>= 100 Pitches)")
```

#Summary Stats Right CT 
```{r}
RightCT <- RightCT[c(2:6, 9, 11, 13, 18, 19)]

RightCT$ExAVG <- as.numeric(as.character(RightCT$ExAVG))
RightCT$ExSLG <- as.numeric(as.character(RightCT$ExSLG))
RightCT$Miss. <- as.numeric(as.character(RightCT$Miss.))
RightCT$K. <- as.numeric(as.character(RightCT$K.))
RightCT$Vel <- as.numeric(as.character(RightCT$Vel))
RightCT$TMIndVertBrk <- as.numeric(as.character(RightCT$TMIndVertBrk))

RightCT <- na.omit(RightCT)

RightCT1 <- filter(RightCT, P > 24)


RightCT1 %>%
  stargazer(type = "text",
            summary.stat = c("N", "median", "mean", "min", "max", "p25", "p75"),
            title = "Right Handed Pitcher's CT (>= 100 Pitches)")
```

#Summary Stats Left CT
```{r}
LeftCT <- LeftCT[c(2:6, 9, 11, 13, 18, 19)]

LeftCT$ExAVG <- as.numeric(as.character(LeftCT$ExAVG))
LeftCT$ExSLG <- as.numeric(as.character(LeftCT$ExSLG))
LeftCT$Miss. <- as.numeric(as.character(LeftCT$Miss.))
LeftCT$K. <- as.numeric(as.character(LeftCT$K.))
LeftCT$Vel <- as.numeric(as.character(LeftCT$Vel))
LeftCT$TMIndVertBrk <- as.numeric(as.character(LeftCT$TMIndVertBrk))

LeftCT <- na.omit(LeftCT)

LeftCT1 <- filter(LeftCT, P > 24)


LeftCT %>%
  stargazer(type = "text",
            summary.stat = c("N", "median", "mean", "min", "max", "p25", "p75"),
            title = "Left Handed Pitcher's CT (>= 100 Pitches)")
```

#Depended Variable Analysis Load Datasets
```{r}
WinningPerc <- read.csv("FanGraphs Leaderboard 2022 Team Pitching copy.csv")
StrikoutPerc <- read.csv("FanGraphs Leaderboard (2).csv")
DepVar <- read.csv("Team Data.csv")
```

#Clean Data
```{r}
WinningPerc <- WinningPerc[c(1, 21)]
StrikoutPerc <- StrikoutPerc[c(1,6)]
DepVar <- DepVar[c(1, 24:25)]
merged <- merge(WinningPerc, DepVar, by = "Team")
merged1 <- merge(WinningPerc, StrikoutPerc, by = "Team")
```

#Visualize XBA and Winning Percentage
```{r}
library(mlbplotR)
library(ggplot2)
library(mlbplotR)
library(ggpubr)

filtered_stats <- merged %>%
  filter(Team != "---")

filtered_stats %>% 
  ggplot(aes(x = XBA, y = Winning.Perc)) +
  geom_smooth(method = "lm", se=FALSE, color="black", formula = y ~ x) +
  geom_mlb_logos(aes(team_abbr = Team), width = 0.06, alpha = 0.6) +
  labs(title = "2022 MLB Winning % and Pitcher Expected Batting Average",
       y = "Winning Percentage",
       x = "XBA",
       caption = "Data: FanGraphs | Riley Feltner || Logos: mlbplotR")+
  coord_cartesian(ylim = c(0.3, 0.7))+
  theme_minimal()+
  stat_cor(aes(label = ..rr.label..), color = "red", geom = "label", label.y.npc = "bottom")
```
#Visualize XSLG and Winning Percentage
```{r}
filtered_stats <- merged %>%
  filter(Team != "---")

filtered_stats %>% 
  ggplot(aes(x = XSLG, y = Winning.Perc)) +
  geom_smooth(method = "lm", se=FALSE, color="black", formula = y ~ x) +
  geom_mlb_logos(aes(team_abbr = Team), width = 0.06, alpha = 0.6) +
  labs(title = "2022 MLB Winning % and Pitcher Expected Slugging %",
       y = "Winning Percentage",
       x = "XSLG",
       caption = "Data: FanGraphs | Riley Feltner || Logos: mlbplotR")+
  coord_cartesian(ylim = c(0.3, 0.7))+
  theme_minimal()+
  stat_cor(aes(label = ..rr.label..), color = "red", geom = "label", label.y.npc = "bottom")
```

#Visualize K% and Winning Percentage
```{r}
filtered_stats <- merged1 %>%
  filter(Team != "---")

filtered_stats %>% 
  ggplot(aes(x = K.Perc, y = Winning.Perc)) +
  geom_smooth(method = "lm", se=FALSE, color="black", formula = y ~ x) +
  geom_mlb_logos(aes(team_abbr = Team), width = 0.06, alpha = 0.6) +
  labs(title = "2022 MLB Winning % and Pitcher Strikeout %",
       y = "Winning Percentage",
       x = "Strikeout Percentage",
       caption = "Data: FanGraphs | Riley Feltner || Logos: mlbplotR")+
  coord_cartesian(ylim = c(0.3, 0.7))+
  theme_minimal()+
  stat_cor(aes(label = ..rr.label..), color = "red", geom = "label")
```


```{r}
library(tidyverse)
library(Hmisc)

#RightFB Binned Heatmap Count
  ggplot(data = RightFB1, mapping = aes(x = TMHrzBrk, y = TMIndVertBrk))+
   geom_bin_2d(bins = 12 )+
   scale_fill_gradient(low = "green", high = "red")+
   ylim(5, 20)+
   xlim(-5,15)+
   coord_fixed(1.3)+
    labs(title = "Right FB >= 25 P",
         subtitle = "MLB 2022",
         x = "Horizontal Break",
         y = "Vertical Break",
         caption = "Sample Size: 495")


 #LeftFB Binned Heatmap Count
  ggplot(data = LeftFB1, mapping = aes(x = TMHrzBrk, y = TMIndVertBrk))+
   geom_bin_2d(bins = 12 )+
   scale_fill_gradient(low = "green", high = "red")+
   coord_fixed(1.3)+
    labs(title = "Left FB >= 25 P",
         subtitle = "MLB 2022",
         x = "Horizontal Break",
         y = "Vertical Break",
         caption = "Sample Size: 168") 
  

  #RightSI Binned Heatmap Count
  ggplot(data = RightSI1, mapping = aes(x = TMHrzBrk, y = TMIndVertBrk))+
   geom_bin_2d(bins = 12)+
   scale_fill_gradient(low = "green", high = "red")+
   coord_fixed(1)+
    labs(title = "Right SI >= 25 P",
         subtitle = "MLB 2022",
         x = "Horizontal Break",
         y = "Vertical Break",
         caption = "Sample Size: 290")  
  
 
  #LeftSI Binned Heatmap Count
  ggplot(data = LeftSI1, mapping = aes(x = TMHrzBrk, y = TMIndVertBrk))+
   geom_bin_2d(bins = 12)+
   scale_fill_gradient(low = "green", high = "red")+
   coord_fixed(1)+
    labs(title = "Left SI >= 25 P",
         subtitle = "MLB 2022",
         x = "Horizontal Break",
         y = "Vertical Break",
         caption = "Sample Size: 105") 
  
  #RightCT Binned Heatmap Count
  ggplot(data = RightCT1, mapping = aes(x = TMHrzBrk, y = TMIndVertBrk))+
   geom_bin_2d(bins = 12)+
   scale_fill_gradient(low = "green", high = "red")+
   coord_fixed(1)+
    labs(title = "Righthanded CT >= 25 P",
         subtitle = "MLB 2022",
         x = "Horizontal Break",
         y = "Vertical Break",
         caption = "Sample Size: 136") 
  
  #LeftCT Binned Heatmap Count
  ggplot(data = LeftCT1, mapping = aes(x = TMHrzBrk, y = TMIndVertBrk))+
   geom_bin_2d(bins = 12)+
   scale_fill_gradient(low = "green", high = "red")+
   coord_fixed(1)+
    labs(title = "Lefthanded CT >= 25 P",
         subtitle = "MLB 2022",
         x = "Horizontal Break",
         y = "Vertical Break",
         caption = "Sample Size: 50")  
```
#Just me trying to determine what ranges to roll with for velo, VB, HB
```{r}
#RHP VB Categories
VLowVB <- filter(RightFB1, TMIndVertBrk <= 10) #18
LowVB <- filter(RightFB1, between(TMIndVertBrk, 10.1, 12.0)) #21
Dead <- filter(RightFB1, between(TMIndVertBrk, 12.1, 15.0)) #131
HighVB <- filter(RightFB1, between(TMIndVertBrk, 15.1, 18)) #242
VHighVB <- filter(RightFB1, TMIndVertBrk >= 18.1) #83

# RHP Velo Categories
VLowVel <- filter(RightFB1, Vel <= 91) #57
LowVel <- filter(RightFB1, between(Vel, 91.1, 93.0)) #102
AvgVel <- filter(RightFB1, between(Vel, 93.1, 95)) #173
HighVel <- filter(RightFB1, between(Vel, 95.1, 97)) #123
VHighVel <- filter(RightFB1, Vel >= 97.1) #41

#RHP HB Categories
VLowHB <- filter(RightFB1, TMHrzBrk <= 3) #53
LowHB <- filter(RightFB1, between(TMHrzBrk, 3.1, 6)) #112
AVGHB <- filter(RightFB1, between(TMHrzBrk, 6.1, 8)) #107
HighHB <- filter(RightFB1, between(TMHrzBrk, 8.1, 10)) #98
VHighHB <- filter(RightFB1, TMHrzBrk >= 10.1) #125

#LHP VB Categories
LHPVLowVB <- filter(LeftFB1, TMIndVertBrk <= 10) #4
LHPLowVB <- filter(LeftFB1, between(TMIndVertBrk, 10.1, 12.0)) #6
LHPDead <- filter(LeftFB1, between(TMIndVertBrk, 12.1, 15.0)) #50
LHPHighVB <- filter(LeftFB1, between(TMIndVertBrk, 15.1, 18)) #87
LHPVHighVB <- filter(LeftFB1, TMIndVertBrk >= 18.1) #21

#LHP HB Categories
LHPVLowHB <- filter(LeftFB1, TMHrzBrk >= -3) #19
LHPLowHB <- filter(LeftFB1, between(TMHrzBrk, -6, -3.1)) #32
LHPAVGHB <- filter(LeftFB1, between(TMHrzBrk, -8, -6.1)) #39
LHPHighHB <- filter(LeftFB1, between(TMHrzBrk, -10, -8.1)) #25
LHPVHighHB <- filter(LeftFB1, TMHrzBrk <= -10.1) #53

#LHP Velo Categories
LHPVLowVel <- filter(LeftFB1, Vel <= 91) #33
LHPLowVel <- filter(LeftFB1, between(Vel, 91.1, 93.0)) #52
LHPAvgVel <- filter(LeftFB1, between(Vel, 93.1, 95)) #58
LHPHighVel <- filter(LeftFB1, between(Vel, 95.1, 97)) #23
LHPVHighVel <- filter(LeftFB1, Vel >= 97.1) #2
```

#Very Low Velo RH FB
```{r}
#Very Low Velocity Category and Very Low VB
library(dplyr)
RightFBVeryLowVBVeryLowHBVeryLowVel <- filter(RightFB1, TMIndVertBrk <= 10, TMHrzBrk <= 3, Vel <=91)
    mean(RightFBVeryLowVBVeryLowHBVeryLowVel$ExAVG)
    count(RightFBVeryLowVBVeryLowHBVeryLowVel)

RightFBVeryLowVBLowHBVeryLowVel <- filter(RightFB1, TMIndVertBrk <= 10, between(TMHrzBrk, 3.1, 6), Vel <=91)
    mean(RightFBVeryLowVBLowHBVeryLowVel$ExAVG)
    count(RightFBVeryLowVBLowHBVeryLowVel$ExAVG)

RightFBVeryLowVBAvgHBVeryLowVel <- filter(RightFB1, TMIndVertBrk <= 10, between(TMHrzBrk, 6.1, 8), Vel <=91)
    mean(RightFBVeryLowVBAvgHBVeryLowVel$ExAVG)
    count(RightFBVeryLowVBAvgHBVeryLowVel$ExAVG)

RightFBVeryLowVBHighHBVeryLowVel <- filter(RightFB1, TMIndVertBrk <= 10, between(TMHrzBrk, 8.1, 10), Vel <=91)
    mean(RightFBVeryLowVBHighHBVeryLowVel$ExAVG)
    count(RightFBVeryLowVBHighHBVeryLowVel$ExAVG)

RightFBVeryLowVBVeryHighHBVeryLowVel <- filter(RightFB1, TMIndVertBrk <= 10, TMHrzBrk >= 10.1, Vel <=91)
  mean(RightFBVeryLowVBVeryHighHBVeryLowVel$ExAVG)
  count(RightFBVeryLowVBVeryHighHBVeryLowVel$ExAVG)


#Very Low Velocity Category and Low VB
  
RightFBLowVBVeryLowHBVeryLowVel <- filter(RightFB1, between(TMIndVertBrk, 10.1, 12), TMHrzBrk <=3, Vel <=91)
    mean(RightFBLowVBVeryLowHBVeryLowVel$ExAVG)
    count(RightFBLowVBVeryLowHBVeryLowVel$ExAVG)
    
RightFBLowVBLowHBVeryLowVel <- filter(RightFB1, between(TMIndVertBrk, 10.1, 12), between(TMHrzBrk, 3.1, 6), Vel <=91)
    mean(RightFBLowVBLowHBVeryLowVel$ExAVG)
    count(RightFBLowVBLowHBVeryLowVel$ExAVG)

RightFBLowVBAvgHBVeryLowVel <- filter(RightFB1, between(TMIndVertBrk, 10.1, 12), between(TMHrzBrk, 6.1, 8), Vel <=91)
    mean(RightFBLowVBAvgHBVeryLowVel$ExAVG)
    count(RightFBLowVBAvgHBVeryLowVel$ExAVG)

RightFBLowVBHighHBVeryLowVel <- filter(RightFB1, between(TMIndVertBrk, 10.1, 12), between(TMHrzBrk, 8.1, 10), Vel <=91)
    mean(RightFBLowVBHighHBVeryLowVel$ExAVG)
    count(RightFBLowVBHighHBVeryLowVel$ExAVG)

RightFBLowVBVeryHighHBVeryLowVel <- filter(RightFB1, between(TMIndVertBrk, 10.1, 12), TMHrzBrk >= 10.1, Vel <=91)
    mean(RightFBLowVBVeryHighHBVeryLowVel$ExAVG)
    count(RightFBLowVBVeryHighHBVeryLowVel$ExAVG)


#Very Low Velocity Category and Dead VB
RightFBDeadVBVeryLowHBVeryLowVel <- filter(RightFB1, between(TMIndVertBrk, 12.1, 15), TMHrzBrk <=3, Vel <= 91)
    mean(RightFBDeadVBVeryLowHBVeryLowVel$ExAVG)
    count(RightFBDeadVBVeryLowHBVeryLowVel)

RightFBDeadVBLowHBVeryLowVel <- filter(RightFB1, between(TMIndVertBrk, 12.1, 15), between(TMHrzBrk, 3.1, 6), Vel <= 91)
    mean(RightFBDeadVBLowHBVeryLowVel$ExAVG)
    count(RightFBDeadVBLowHBVeryLowVel$ExAVG)

RightFBDeadVBAvgHBVeryLowVel <- filter(RightFB1, between(TMIndVertBrk, 12.1, 15), between(TMHrzBrk, 6.1, 8), Vel <= 91)
    mean(RightFBDeadVBAvgHBVeryLowVel$ExAVG)
    count(RightFBDeadVBAvgHBVeryLowVel$ExAVG)
    
RightFBDeadVBHighHBVeryLowVel <- filter(RightFB1, between(TMIndVertBrk, 12.1, 15), between(TMHrzBrk, 8.1, 10), Vel <= 91)
    mean(RightFBDeadVBHighHBVeryLowVel$ExAVG)
    count(RightFBDeadVBHighHBVeryLowVel$ExAVG)
    
RightFBDeadVBVeryHighHBVeryLowVel <- filter(RightFB1, between(TMIndVertBrk, 12.1, 15), TMHrzBrk >= 10.1, Vel <= 91)
    mean(RightFBDeadVBVeryHighHBVeryLowVel$ExAVG)
    count(RightFBDeadVBVeryHighHBVeryLowVel)


#Very Low Velocity Category and High VB
RightFBHighVBVeryLowHBVeryLowVel <- filter(RightFB1, between(TMIndVertBrk, 15.1, 18), TMHrzBrk <=3, Vel <= 91)
    mean(RightFBHighVBVeryLowHBVeryLowVel$ExAVG)
    count(RightFBHighVBVeryLowHBVeryLowVel$ExAVG)

RightFBHighVBLowHBVeryLowVel <- filter(RightFB1, between(TMIndVertBrk, 15.1, 18), between(TMHrzBrk, 3.1, 6), Vel <= 91)
    mean(RightFBHighVBLowHBVeryLowVel$ExAVG)
    count(RightFBHighVBLowHBVeryLowVel$ExAVG)

RightFBHighVBAvgHBVeryLowVel <- filter(RightFB1, between(TMIndVertBrk, 15.1, 18), between(TMHrzBrk, 6.1, 8), Vel <= 91)
    mean(RightFBHighVBAvgHBVeryLowVel$ExAVG)
    count(RightFBHighVBAvgHBVeryLowVel$ExAVG)
    
RightFBHighVBHighHBVeryLowVel <- filter(RightFB1, between(TMIndVertBrk, 15.1, 18), between(TMHrzBrk, 8.1, 10), Vel <= 91)
    mean(RightFBHighVBHighHBVeryLowVel$ExAVG)
    count(RightFBHighVBHighHBVeryLowVel$ExAVG)
    
RightFBHighVBVeryHighHBVeryLowVel <- filter(RightFB1, between(TMIndVertBrk, 15.1, 18), TMHrzBrk >= 10.1, Vel <= 91)
    mean(RightFBHighVBVeryHighHBVeryLowVel$ExAVG)
    count(RightFBHighVBVeryHighHBVeryLowVel$ExAVG)

#Very Low Velocity Category and Very High VB
RightFBVeryHighVBVeryLowHBVeryLowVel <- filter(RightFB1, TMIndVertBrk >= 18.1, TMHrzBrk <= 3,Vel <= 91)
    mean(RightFBVeryHighVBVeryLowHBVeryLowVel$ExAVG)
    count(RightFBVeryHighVBVeryLowHBVeryLowVel$ExAVG)

RightFBVeryHighVBLowHBVeryLowVel <- filter(RightFB1, TMIndVertBrk >= 18.1, between(TMHrzBrk, 3.1, 6),Vel <= 91)
    mean(RightFBVeryHighVBLowHBVeryLowVel$ExAVG)
    count(RightFBVeryHighVBLowHBVeryLowVel$ExAVG)

RightFBVeryHighVBAvgHBVeryLowVel <- filter(RightFB1, TMIndVertBrk >= 18.1, between(TMHrzBrk, 6.1, 8),Vel <= 91)
    mean(RightFBVeryHighVBAvgHBVeryLowVel$ExAVG)
    count(RightFBVeryHighVBAvgHBVeryLowVel$ExAVG)
    
RightFBVeryHighVBHighHBVeryLowVel <- filter(RightFB1, TMIndVertBrk >= 18.1, between(TMHrzBrk, 8.1, 10),Vel <= 91)
    mean(RightFBVeryHighVBHighHBVeryLowVel$ExAVG)
    count(RightFBVeryHighVBHighHBVeryLowVel$ExAVG)
    
RightFBVeryHighVBVeryHighHBVeryLowVel <- filter(RightFB1, TMIndVertBrk >= 18.1, TMHrzBrk >= 10.1,Vel <= 91)
    mean(RightFBVeryHighVBVeryHighHBVeryLowVel$ExAVG)
    count(RightFBVeryHighVBVeryHighHBVeryLowVel$ExAVG)
    
mean(RightFB1$ExAVG)
quantile(LeftFB1$ExAVG, probs = c(0.10, 0.50, 0.90))
```


#Low Velo RH FB
```{r}
#Low Velocity Category and Very Low VB
RightFBVeryLowVBVeryLowHBLowVel <- filter(RightFB1, TMIndVertBrk <= 10, TMHrzBrk <= 3, between(Vel, 91.1, 93))
    mean(RightFBVeryLowVBVeryLowHBLowVel$ExAVG)
    count(RightFBVeryLowVBVeryLowHBLowVel$ExAVG)
    
RightFBVeryLowVBLowHBLowVel <- filter(RightFB1, TMIndVertBrk <= 10, between(TMHrzBrk, 3.1, 6), between(Vel, 91.1, 93))
    mean(RightFBVeryLowVBLowHBLowVel$ExAVG)
    count(RightFBVeryLowVBLowHBLowVel$ExAVG)
    
RightFBVeryLowVBAvgHBLowVel <- filter(RightFB1, TMIndVertBrk <= 10, between(TMHrzBrk, 6.1, 8), between(Vel, 91.1, 93))
    mean(RightFBVeryLowVBAvgHBLowVel$ExAVG)
    count(RightFBVeryLowVBAvgHBLowVel$ExAVG)
    
RightFBVeryLowVBHighHBLowVel <- filter(RightFB1, TMIndVertBrk <= 10, between(TMHrzBrk, 8.1, 10), between(Vel, 91.1, 93))
    mean(RightFBVeryLowVBHighHBLowVel$ExAVG)
    count(RightFBVeryLowVBHighHBLowVel$ExAVG)
    
RightFBVeryLowVBVeryHighHBLowVel <- filter(RightFB1, TMIndVertBrk <= 10, TMHrzBrk >= 10.1, between(Vel, 91.1, 93))
    mean(RightFBVeryLowVBVeryHighHBLowVel$ExAVG)
    count(RightFBVeryLowVBVeryHighHBLowVel$ExAVG)

#Low Velocity Category and Low VB
RightFBLowVBVeryLowHBLowVel <- filter(RightFB1, between(TMIndVertBrk, 10.1, 12), TMHrzBrk <= 3, between(Vel, 91.3, 93))
    mean(RightFBLowVBVeryLowHBLowVel$ExAVG)
    count(RightFBLowVBVeryLowHBLowVel$ExAVG)
    
RightFBLowVBLowHBLowVel <- filter(RightFB1, between(TMIndVertBrk, 10.1, 12), between(TMHrzBrk, 3.1, 6), between(Vel, 91.1, 93))
    mean(RightFBLowVBLowHBLowVel$ExAVG)
    count(RightFBLowVBLowHBLowVel$ExAVG)
    
RightFBLowVBAvgHBLowVel <- filter(RightFB1, between(TMIndVertBrk, 10.1, 12), between(TMHrzBrk, 6.1, 8), between(Vel, 91.1, 93))
    mean(RightFBLowVBAvgHBLowVel$ExAVG)
    count(RightFBLowVBAvgHBLowVel$ExAVG)

RightFBLowVBHighHBLowVel <- filter(RightFB1, between(TMIndVertBrk, 10.1, 12), between(TMHrzBrk, 8.1, 10), between(Vel, 91.1, 93))
    mean(RightFBLowVBHighHBLowVel$ExAVG)
    count(RightFBLowVBHighHBLowVel$ExAVG)

RightFBLowVBVeryHighHBLowVel <- filter(RightFB1, between(TMIndVertBrk, 10.1, 12), TMHrzBrk >= 10.1, between(Vel, 91.1, 93))
    mean(RightFBLowVBVeryHighHBLowVel$ExAVG)
    count(RightFBLowVBVeryHighHBLowVel$ExAVG)

#Low Velocity Category and Dead VB
RightFBDeadVBVeryLowHBLowVel <- filter(RightFB1, between(TMIndVertBrk, 12.1, 15), TMHrzBrk <= 3, between(Vel, 91.3, 93))
    mean(RightFBDeadVBVeryLowHBLowVel$ExAVG)
    count(RightFBDeadVBVeryLowHBLowVel$ExAVG)

RightFBDeadVBLowHBLowVel <- filter(RightFB1, between(TMIndVertBrk, 12.1, 15), between(TMHrzBrk, 3.1, 6), between(Vel, 91.1, 93))
    mean(RightFBDeadVBLowHBLowVel$ExAVG)
    count(RightFBDeadVBLowHBLowVel$ExAVG)

RightFBDeadVBAvgHBLowVel <- filter(RightFB1, between(TMIndVertBrk, 12.1, 15), between(TMHrzBrk, 6.1, 8), between(Vel, 91.1, 93))
    mean(RightFBDeadVBAvgHBLowVel$ExAVG)
    count(RightFBDeadVBAvgHBLowVel$ExAVG)

RightFBDeadVBHighHBLowVel <- filter(RightFB1, between(TMIndVertBrk, 12.1, 15), between(TMHrzBrk, 8.1, 10), between(Vel, 91.1, 93))
    mean(RightFBDeadVBHighHBLowVel$ExAVG)
    count(RightFBDeadVBHighHBLowVel$ExAVG)

RightFBDeadVBVeryHighHBLowVel <- filter(RightFB1, between(TMIndVertBrk, 12.1, 15), TMHrzBrk >= 10.1, between(Vel, 91.1, 93))
    mean(RightFBDeadVBVeryHighHBLowVel$ExAVG)
    count(RightFBDeadVBVeryHighHBLowVel$ExAVG)

#Low Velocity Category and High VB
RightFBHighVBVeryLowHBLowVel <- filter(RightFB1, between(TMIndVertBrk, 15.1, 18), TMHrzBrk <= 3, between(Vel, 91.3, 93))
    mean(RightFBHighVBVeryLowHBLowVel$ExAVG)
    count(RightFBHighVBVeryLowHBLowVel$ExAVG)

RightFBHighVBLowHBLowVel <- filter(RightFB1, between(TMIndVertBrk, 15.1, 18), between(TMHrzBrk, 3.1, 6), between(Vel, 91.1, 93))
    mean(RightFBHighVBLowHBLowVel$ExAVG)
    count(RightFBHighVBLowHBLowVel$ExAVG)

RightFBHighVBAvgHBLowVel <- filter(RightFB1, between(TMIndVertBrk, 15.1, 18), between(TMHrzBrk, 6.1, 8), between(Vel, 91.1, 93))
    mean(RightFBHighVBAvgHBLowVel$ExAVG)
    count(RightFBHighVBAvgHBLowVel$ExAVG)

RightFBHighVBHighHBLowVel <- filter(RightFB1, between(TMIndVertBrk, 15.1, 18), between(TMHrzBrk, 8.1, 10), between(Vel, 91.1, 93))
    mean(RightFBHighVBHighHBLowVel$ExAVG)
    count(RightFBHighVBHighHBLowVel$ExAVG)

RightFBHighVBVeryHighHBLowVel <- filter(RightFB1, between(TMIndVertBrk, 15.1, 18), TMHrzBrk >= 10.1, between(Vel, 91.1, 93))
    mean(RightFBHighVBVeryHighHBLowVel$ExAVG)
    count(RightFBHighVBVeryHighHBLowVel$ExAVG)

#Low Velocity Category and Very High VB
RightFBVeryHighVBVeryLowHBLowVel <- filter(RightFB1, TMIndVertBrk >= 18.1, TMHrzBrk <= 3, between(Vel, 91.1, 93))
    mean(RightFBVeryHighVBVeryLowHBLowVel$ExAVG)
    count(RightFBVeryHighVBVeryLowHBLowVel$ExAVG)

RightFBVeryHighVBLowHBLowVel <- filter(RightFB1, TMIndVertBrk >= 18.1, between(TMHrzBrk, 3.1, 6), between(Vel, 91.1, 93))
    mean(RightFBVeryHighVBLowHBLowVel$ExAVG)
    count(RightFBVeryHighVBLowHBLowVel$ExAVG)

RightFBVeryHighVBAvgHBLowVel <- filter(RightFB1, TMIndVertBrk >= 18.1, between(TMHrzBrk, 6.1, 8), between(Vel, 91.1, 93))
    mean(RightFBVeryHighVBAvgHBLowVel$ExAVG)
    count(RightFBVeryHighVBAvgHBLowVel$ExAVG)
    
RightFBVeryHighVBHighHBLowVel <- filter(RightFB1, TMIndVertBrk >= 18.1, between(TMHrzBrk, 8.1, 10), between(Vel, 91.1, 93))
    mean(RightFBVeryHighVBHighHBLowVel$ExAVG)
    count(RightFBVeryHighVBHighHBLowVel$ExAVG)

RightFBVeryHighVBVeryHighHBLowVel <- filter(RightFB1, TMIndVertBrk >= 18.1, TMHrzBrk >= 10.1, between(Vel, 91.1, 93))
    mean(RightFBVeryHighVBVeryHighHBLowVel$ExAVG)
    count(RightFBVeryHighVBVeryHighHBLowVel$ExAVG)

```

#Average Vel RH FB
```{r}
#Avg Velocity Category and Very Low VB
RightFBVeryLowVBVeryLowHBAvgVel <- filter(RightFB1, TMIndVertBrk <= 10, TMHrzBrk <= 3, between(Vel, 93.1, 95))
    mean(RightFBVeryLowVBVeryLowHBAvgVel$ExAVG)
    count(RightFBVeryLowVBVeryLowHBAvgVel)

RightFBVeryLowVBLowHBAvgVel <- filter(RightFB1, TMIndVertBrk <= 10, between(TMHrzBrk, 3.1, 6), between(Vel, 93.1, 95))
    mean(RightFBVeryLowVBLowHBAvgVel$ExAVG)
    count(RightFBVeryLowVBLowHBAvgVel)

RightFBVeryLowVBAvgHBAvgVel <- filter(RightFB1, TMIndVertBrk <= 10, between(TMHrzBrk, 6.1, 8), between(Vel, 93.1, 95))
    mean(RightFBVeryLowVBAvgHBAvgVel$ExAVG)
    count(RightFBVeryLowVBAvgHBAvgVel)

RightFBVeryLowVBHighHBAvgVel <- filter(RightFB1, TMIndVertBrk <= 10, between(TMHrzBrk, 8.1, 10), between(Vel, 93.1, 95))
    mean(RightFBVeryLowVBHighHBAvgVel$ExAVG)
    count(RightFBVeryLowVBHighHBAvgVel)

RightFBVeryLowVBVeryHighHBAvgVel <- filter(RightFB1, TMIndVertBrk <= 10, TMHrzBrk >= 10.1, between(Vel, 93.1, 95))
    mean(RightFBVeryLowVBVeryHighHBAvgVel$ExAVG)
    count(RightFBVeryLowVBVeryHighHBAvgVel)


#Avg Velocity Category and Low VB
RightFBLowVBVeryLowHBAvgVel <- filter(RightFB1, between(TMIndVertBrk, 10.1, 12), TMHrzBrk <= 3, between(Vel, 93.1, 95))
    mean(RightFBLowVBVeryLowHBAvgVel$ExAVG)
    count(RightFBLowVBVeryLowHBAvgVel)

RightFBLowVBLowHBAvgVel <- filter(RightFB1, between(TMIndVertBrk, 10.1, 12), between(TMHrzBrk, 3.1, 6), between(Vel, 93.1, 95))
    mean(RightFBLowVBLowHBAvgVel$ExAVG)
    count(RightFBLowVBLowHBAvgVel)

RightFBLowVBAvgHBAvgVel <- filter(RightFB1, between(TMIndVertBrk, 10.1, 12), between(TMHrzBrk, 6.1, 8), between(Vel, 93.1, 95))
    mean(RightFBLowVBAvgHBAvgVel$ExAVG)
    count(RightFBLowVBAvgHBAvgVel)
    
RightFBLowVBHighHBAvgVel <- filter(RightFB1, between(TMIndVertBrk, 10.1, 12), between(TMHrzBrk, 8.1, 10), between(Vel, 93.1, 95))
    mean(RightFBLowVBHighHBAvgVel$ExAVG)
    count(RightFBLowVBHighHBAvgVel)

RightFBLowVBVeryHighHBAvgVel <- filter(RightFB1, between(TMIndVertBrk, 10.1, 12), TMHrzBrk >= 10.1, between(Vel, 93.1, 95))
    mean(RightFBLowVBVeryHighHBAvgVel$ExAVG)
    count(RightFBLowVBVeryHighHBAvgVel)

#Avg Velocity Category and Dead VB
RightFBDeadVBVeryLowHBAvgVel <- filter(RightFB1, between(TMIndVertBrk, 12.1, 15), TMHrzBrk <= 3, between(Vel, 93.1, 95))
    mean(RightFBDeadVBVeryLowHBAvgVel$ExAVG)
    count(RightFBDeadVBVeryLowHBAvgVel)

RightFBDeadVBLowHBAvgVel <- filter(RightFB1, between(TMIndVertBrk, 12.1, 15), between(TMHrzBrk, 3.1, 6), between(Vel, 93.1, 95))
    mean(RightFBDeadVBLowHBAvgVel$ExAVG)
    count(RightFBDeadVBLowHBAvgVel)

RightFBDeadVBAvgHBAvgVel <- filter(RightFB1, between(TMIndVertBrk, 12.1, 15), between(TMHrzBrk, 6.1, 8), between(Vel, 93.1, 95))
    mean(RightFBDeadVBAvgHBAvgVel$ExAVG)
    count(RightFBDeadVBAvgHBAvgVel)

RightFBDeadVBHighHBAvgVel <- filter(RightFB1, between(TMIndVertBrk, 12.1, 15), between(TMHrzBrk, 8.1, 10), between(Vel, 93.1, 95))
    mean(RightFBDeadVBHighHBAvgVel$ExAVG)
    count(RightFBDeadVBHighHBAvgVel)

RightFBDeadVBVeryHighHBAvgVel <- filter(RightFB1, between(TMIndVertBrk, 12.1, 15), TMHrzBrk >= 10.1, between(Vel, 93.1, 95))
    mean(RightFBDeadVBVeryHighHBAvgVel$ExAVG)
    count(RightFBDeadVBVeryHighHBAvgVel)

#Avg Velocity Category and High VB
RightFBHighVBVeryLowHBAvgVel <- filter(RightFB1, between(TMIndVertBrk, 15.1, 18), TMHrzBrk <= 3, between(Vel, 93.1, 95))
    mean(RightFBHighVBVeryLowHBAvgVel$ExAVG)
    count(RightFBHighVBVeryLowHBAvgVel)

RightFBHighVBLowHBAvgVel <- filter(RightFB1, between(TMIndVertBrk, 15.1, 18), between(TMHrzBrk, 3.1, 6), between(Vel, 93.1, 95))
    mean(RightFBHighVBLowHBAvgVel$ExAVG)
    count(RightFBHighVBLowHBAvgVel)

RightFBHighVBAvgHBAvgVel <- filter(RightFB1, between(TMIndVertBrk, 15.1, 18), between(TMHrzBrk, 6.1, 8), between(Vel, 93.1, 95))
    mean(RightFBHighVBAvgHBAvgVel$ExAVG)
    count(RightFBHighVBAvgHBAvgVel)

RightFBHighVBHighHBAvgVel <- filter(RightFB1, between(TMIndVertBrk, 15.1, 18), between(TMHrzBrk, 8.1, 10), between(Vel, 93.1, 95))
    mean(RightFBHighVBHighHBAvgVel$ExAVG)
    count(RightFBHighVBHighHBAvgVel)

RightFBHighVBVeryHighHBAvgVel <- filter(RightFB1, between(TMIndVertBrk, 15.1, 18), TMHrzBrk >= 10.1, between(Vel, 93.1, 95))
    mean(RightFBHighVBVeryHighHBAvgVel$ExAVG)
    count(RightFBHighVBVeryHighHBAvgVel)

#Avg Velocity Category and Very High VB
RightFBVeryHighVBVeryLowHBAvgVel <- filter(RightFB1, TMIndVertBrk >= 18.1, TMHrzBrk <= 3, between(Vel, 93.1, 95))
    mean(RightFBVeryHighVBVeryLowHBAvgVel$ExAVG)
    count(RightFBVeryHighVBVeryLowHBAvgVel)

RightFBVeryHighVBLowHBAvgVel <- filter(RightFB1, TMIndVertBrk >= 18.1, between(TMHrzBrk, 3.1, 6), between(Vel, 93.1, 95))
    mean(RightFBVeryHighVBLowHBAvgVel$ExAVG)
    count(RightFBVeryHighVBLowHBAvgVel)

RightFBVeryHighVBAvgHBAvgVel <- filter(RightFB1, TMIndVertBrk >= 18.1, between(TMHrzBrk, 6.1, 8), between(Vel, 93.1, 95))
    mean(RightFBVeryHighVBAvgHBAvgVel$ExAVG)
    count(RightFBVeryHighVBAvgHBAvgVel)

RightFBVeryHighVBHighHBAvgVel <- filter(RightFB1, TMIndVertBrk >= 18.1, between(TMHrzBrk, 8.1, 10), between(Vel, 93.1, 95))
    mean(RightFBVeryHighVBHighHBAvgVel$ExAVG)
    count(RightFBVeryHighVBHighHBAvgVel)

RightFBVeryHighVBVeryHighHBAvgVel <- filter(RightFB1, TMIndVertBrk >= 18.1, TMHrzBrk >= 10.1, between(Vel, 93.1, 95))
    mean(RightFBVeryHighVBVeryHighHBAvgVel$ExAVG)
    count(RightFBVeryHighVBVeryHighHBAvgVel)

```

#High Vel RH FB
```{r}
#High Velocity Category and Very Low VB
RightFBVeryLowVBVeryLowHBHighVel <- filter(RightFB1, TMIndVertBrk <= 10, TMHrzBrk <= 3, between(Vel, 95.1, 97))
  mean(RightFBVeryLowVBVeryLowHBHighVel$ExAVG)
  count(RightFBVeryLowVBVeryLowHBHighVel)

RightFBVeryLowVBLowHBHighVel <- filter(RightFB1, TMIndVertBrk <= 10, between(TMHrzBrk, 3.1, 6), between(Vel, 95.1, 97))
  mean(RightFBVeryLowVBLowHBHighVel$ExAVG)
  count(RightFBVeryLowVBLowHBHighVel)

RightFBVeryLowVBAvgHBHighVel <- filter(RightFB1, TMIndVertBrk <= 10, between(TMHrzBrk, 6.1, 8), between(Vel, 95.1, 97))
    mean(RightFBVeryLowVBAvgHBHighVel$ExAVG)
    count(RightFBVeryLowVBAvgHBHighVel)

RightFBVeryLowVBHighHBHighVel <- filter(RightFB1, TMIndVertBrk <= 10, between(TMHrzBrk, 8.1, 10), between(Vel, 95.1, 97))
    mean(RightFBVeryLowVBHighHBHighVel$ExAVG)
    count(RightFBVeryLowVBHighHBHighVel)

RightFBVeryLowVBVeryHighHBHighVel <- filter(RightFB1, TMIndVertBrk <= 10, TMHrzBrk >= 10.1, between(Vel, 95.1, 97))
    mean(RightFBVeryLowVBVeryHighHBHighVel$ExAVG)
    count(RightFBVeryLowVBVeryHighHBHighVel)

#High Velocity Category and Low VB
RightFBLowVBVeryLowHBHighVel <- filter(RightFB1, between(TMIndVertBrk, 10.1, 12), TMHrzBrk <= 3, between(Vel, 95.1, 97))
    mean(RightFBLowVBVeryLowHBHighVel$ExAVG)
    count(RightFBLowVBVeryLowHBHighVel)

RightFBLowVBLowHBHighVel <- filter(RightFB1, between(TMIndVertBrk, 10.1, 12), between(TMHrzBrk, 3.1, 6), between(Vel, 95.1, 97))
    mean(RightFBLowVBLowHBHighVel$ExAVG)
    count(RightFBLowVBLowHBHighVel)
    
RightFBLowVBAvgHBHighVel <- filter(RightFB1, between(TMIndVertBrk, 10.1, 12), between(TMHrzBrk, 6.1, 8), between(Vel, 95.1, 97))
    mean(RightFBLowVBAvgHBHighVel$ExAVG)
    count(RightFBLowVBAvgHBHighVel)

RightFBLowVBHighHBHighVel <- filter(RightFB1, between(TMIndVertBrk, 10.1, 12), between(TMHrzBrk, 8.1, 10), between(Vel, 95.1, 97))
    mean(RightFBLowVBHighHBHighVel$ExAVG)
    count(RightFBLowVBHighHBHighVel)

RightFBLowVBVeryHighHBHighVel <- filter(RightFB1, between(TMIndVertBrk, 10.1, 12), TMHrzBrk >= 10.1, between(Vel, 95.1, 97))
    mean(RightFBLowVBVeryHighHBHighVel$ExAVG)
    count(RightFBLowVBVeryHighHBHighVel)

#High Velocity Category and Dead VB
RightFBDeadVBVeryLowHBHighVel <- filter(RightFB1, between(TMIndVertBrk, 12.1, 15), TMHrzBrk <= 3, between(Vel, 95.1, 97))
    mean(RightFBDeadVBVeryLowHBHighVel$ExAVG)
    count(RightFBDeadVBVeryLowHBHighVel)

RightFBDeadVBLowHBHighVel <- filter(RightFB1, between(TMIndVertBrk, 12.1, 15), between(TMHrzBrk, 3.1, 6), between(Vel, 95.1, 97))
    mean(RightFBDeadVBLowHBHighVel$ExAVG)
    count(RightFBDeadVBLowHBHighVel)

RightFBDeadVBAvgHBHighVel <- filter(RightFB1, between(TMIndVertBrk, 12.1, 15), between(TMHrzBrk, 6.1, 8), between(Vel, 95.1, 97))
    mean(RightFBDeadVBAvgHBHighVel$ExAVG)
    count(RightFBDeadVBAvgHBHighVel)

RightFBDeadVBHighHBHighVel <- filter(RightFB1, between(TMIndVertBrk, 12.1, 15), between(TMHrzBrk, 8.1, 10), between(Vel, 95.1, 97))
    mean(RightFBDeadVBHighHBHighVel$ExAVG)
    count(RightFBDeadVBHighHBHighVel)

RightFBDeadVBVeryHighHBHighVel <- filter(RightFB1, between(TMIndVertBrk, 12.1, 15), TMHrzBrk >= 10.1, between(Vel, 95.1, 97))
    mean(RightFBDeadVBVeryHighHBHighVel$ExAVG)
    count(RightFBDeadVBVeryHighHBHighVel)

#High Velocity Category and High VB
RightFBHighVBVeryLowHBHighVel <- filter(RightFB1, between(TMIndVertBrk, 15.1, 18), TMHrzBrk <= 3, between(Vel, 95.1, 97))
    mean(RightFBHighVBVeryLowHBHighVel$ExAVG)
    count(RightFBHighVBVeryLowHBHighVel)

RightFBHighVBLowHBHighVel <- filter(RightFB1, between(TMIndVertBrk, 15.1, 18), between(TMHrzBrk, 3.1, 6), between(Vel, 95.1, 97))
    mean(RightFBHighVBLowHBHighVel$ExAVG)
    count(RightFBHighVBLowHBHighVel)

RightFBHighVBAvgHBHighVel <- filter(RightFB1, between(TMIndVertBrk, 15.1, 18), between(TMHrzBrk, 6.1, 8), between(Vel, 95.1, 97))
    mean(RightFBHighVBAvgHBHighVel$ExAVG)
    count(RightFBHighVBAvgHBHighVel)

RightFBHighVBHighHBHighVel <- filter(RightFB1, between(TMIndVertBrk, 15.1, 18), between(TMHrzBrk, 8.1, 10), between(Vel, 95.1, 97))
    mean(RightFBHighVBHighHBHighVel$ExAVG) 
    count(RightFBHighVBHighHBHighVel)

RightFBHighVBVeryHighHBHighVel <- filter(RightFB1, between(TMIndVertBrk, 15.1, 18), TMHrzBrk >= 10.1, between(Vel, 95.1, 97))
    mean(RightFBHighVBVeryHighHBHighVel$ExAVG)
    count(RightFBHighVBVeryHighHBHighVel)

#High Velocity Category and Very High VB
RightFBVeryHighVBVeryLowHBHighVel <- filter(RightFB1, TMIndVertBrk >= 18.1, TMHrzBrk <= 3, between(Vel, 95.1, 97))
    mean(RightFBVeryHighVBVeryLowHBHighVel$ExAVG)
    count(RightFBVeryHighVBVeryLowHBHighVel)

RightFBVeryHighVBLowHBHighVel <- filter(RightFB1, TMIndVertBrk >= 18.1, between(TMHrzBrk, 3.1, 6), between(Vel, 95.1, 97))
    mean(RightFBVeryHighVBLowHBHighVel$ExAVG)
    count(RightFBVeryHighVBLowHBHighVel)

RightFBVeryHighVBAvgHBHighVel <- filter(RightFB1, TMIndVertBrk >= 18.1, between(TMHrzBrk, 6.1, 8), between(Vel, 95.1, 97))
    mean(RightFBVeryHighVBAvgHBHighVel$ExAVG)
    count(RightFBVeryHighVBAvgHBHighVel)

RightFBVeryHighVBHighHBHighVel <- filter(RightFB1, TMIndVertBrk >= 18.1, between(TMHrzBrk, 8.1, 10), between(Vel, 95.1, 97))
    mean(RightFBVeryHighVBHighHBHighVel$ExAVG)
    count(RightFBVeryHighVBHighHBHighVel)

RightFBVeryHighVBVeryHighHBHighVel <- filter(RightFB1, TMIndVertBrk >= 18.1, TMHrzBrk >= 10.1, between(Vel, 95.1, 97))
    mean(RightFBVeryHighVBVeryHighHBHighVel$ExAVG)
    count(RightFBVeryHighVBVeryHighHBHighVel)

```

#Very High Vel RH FB
```{r}
#Very High Velocity Category and Very Low VB
RightFBVeryLowVBVeryLowHBVeryHighVel <- filter(RightFB1, TMIndVertBrk <= 10, TMHrzBrk <= 3, Vel >= 97.1)
    mean(RightFBVeryLowVBVeryLowHBVeryHighVel$ExAVG)
    count(RightFBVeryLowVBVeryLowHBVeryHighVel)

RightFBVeryLowVBLowHBVeryHighVel <- filter(RightFB1, TMIndVertBrk <= 10, between(TMHrzBrk, 3.1, 6), Vel >= 97.1)
    mean(RightFBVeryLowVBLowHBVeryHighVel$ExAVG)
    count(RightFBVeryLowVBLowHBVeryHighVel)

RightFBVeryLowVBAvgHBVeryHighVel <- filter(RightFB1, TMIndVertBrk <= 10, between(TMHrzBrk, 6.1, 8), Vel >= 97.1)
    mean(RightFBVeryLowVBAvgHBVeryHighVel$ExAVG)
    count(RightFBVeryLowVBAvgHBVeryHighVel)

RightFBVeryLowVBHighHBVeryHighVel <- filter(RightFB1, TMIndVertBrk <= 10, between(TMHrzBrk, 8.1, 10), Vel >= 97.1)
    mean(RightFBVeryLowVBHighHBVeryHighVel$ExAVG)
    count(RightFBVeryLowVBHighHBVeryHighVel)

RightFBVeryLowVBVeryHighHBVeryHighVel <- filter(RightFB1, TMIndVertBrk <= 10, TMHrzBrk >= 10.1, Vel >= 97.1)
    mean(RightFBVeryLowVBVeryHighHBVeryHighVel$ExAVG)
    count(RightFBVeryLowVBVeryHighHBVeryHighVel)


#Very High Velocity Category and Low VB
RightFBLowVBVeryLowHBVeryHighVel <- filter(RightFB1, between(TMIndVertBrk, 10.1, 12), TMHrzBrk <= 3, Vel >= 97.1)
    mean(RightFBLowVBVeryLowHBVeryHighVel$ExAVG)
    count(RightFBLowVBVeryLowHBVeryHighVel)

RightFBLowVBLowHBVeryHighVel <- filter(RightFB1, between(TMIndVertBrk, 10.1, 12), between(TMHrzBrk, 3.1, 6), Vel >= 97.1)
    mean(RightFBLowVBLowHBVeryHighVel$ExAVG)
    count(RightFBLowVBLowHBVeryHighVel)

RightFBLowVBAvgHBVeryHighVel <- filter(RightFB1, between(TMIndVertBrk, 10.1, 12), between(TMHrzBrk, 6.1, 8), Vel >= 97.1)
    mean(RightFBLowVBAvgHBVeryHighVel$ExAVG)
    count(RightFBLowVBAvgHBVeryHighVel)

RightFBLowVBHighHBVeryHighVel <- filter(RightFB1, between(TMIndVertBrk, 10.1, 12), between(TMHrzBrk, 8.1, 10), Vel >= 97.1)
    mean(RightFBLowVBHighHBVeryHighVel$ExAVG)
    count(RightFBLowVBHighHBVeryHighVel)

RightFBLowVBVeryHighHBVeryHighVel <- filter(RightFB1, between(TMIndVertBrk, 10.1, 12), TMHrzBrk >= 10.1, Vel >= 97.1)
    mean(RightFBLowVBVeryHighHBVeryHighVel$ExAVG)
    count(RightFBLowVBVeryHighHBVeryHighVel)

#Very High Velocity Category and Dead VB
RightFBDeadVBVeryLowHBVeryHighVel <- filter(RightFB1, between(TMIndVertBrk, 12.1, 15), TMHrzBrk <= 3, Vel >= 97.1)
    mean(RightFBDeadVBVeryLowHBVeryHighVel$ExAVG)
    count(RightFBDeadVBVeryLowHBVeryHighVel)

RightFBDeadVBLowHBVeryHighVel <- filter(RightFB1, between(TMIndVertBrk, 12.1, 15), between(TMHrzBrk, 3.1, 6), Vel >= 97.1)
    mean(RightFBDeadVBLowHBVeryHighVel$ExAVG)
    count(RightFBDeadVBLowHBVeryHighVel)

RightFBDeadVBAvgHBVeryHighVel <- filter(RightFB1, between(TMIndVertBrk, 12.1, 15), between(TMHrzBrk, 6.1, 8), Vel >= 97.1)
    mean(RightFBDeadVBAvgHBVeryHighVel$ExAVG)
    count(RightFBDeadVBAvgHBVeryHighVel)

RightFBDeadVBHighHBVeryHighVel <- filter(RightFB1, between(TMIndVertBrk, 12.1, 15), between(TMHrzBrk, 8.1, 10), Vel >= 97.1)
    mean(RightFBDeadVBHighHBVeryHighVel$ExAVG)
    count(RightFBDeadVBHighHBVeryHighVel)

RightFBDeadVBVeryHighHBVeryHighVel <- filter(RightFB1, between(TMIndVertBrk, 12.1, 15), TMHrzBrk >= 10.1, Vel >= 97.1)
    mean(RightFBDeadVBVeryHighHBVeryHighVel$ExAVG)
    count(RightFBDeadVBVeryHighHBVeryHighVel)

#Very High Velocity Category and High VB
RightFBHighVBVeryLowHBVeryHighVel <- filter(RightFB1, between(TMIndVertBrk, 15.1, 18), TMHrzBrk <= 3, Vel >= 97.1)
    mean(RightFBHighVBVeryLowHBVeryHighVel$ExAVG)
    count(RightFBHighVBVeryLowHBVeryHighVel)

RightFBHighVBLowHBVeryHighVel <- filter(RightFB1, between(TMIndVertBrk, 15.1, 18), between(TMHrzBrk, 3.1, 6), Vel >= 97.1)
    mean(RightFBHighVBLowHBVeryHighVel$ExAVG)
    count(RightFBHighVBLowHBVeryHighVel)

RightFBHighVBAvgHBVeryHighVel <- filter(RightFB1, between(TMIndVertBrk, 15.1, 18), between(TMHrzBrk, 6.1, 8), Vel >= 97.1)
    mean(RightFBHighVBAvgHBVeryHighVel$ExAVG)
    count(RightFBHighVBAvgHBVeryHighVel)

RightFBHighVBHighHBVeryHighVel <- filter(RightFB1, between(TMIndVertBrk, 15.1, 18), between(TMHrzBrk, 8.1, 10), Vel >= 97.1)
    mean(RightFBHighVBHighHBVeryHighVel$ExAVG)
    count(RightFBHighVBHighHBVeryHighVel)

RightFBHighVBVeryHighHBVeryHighVel <- filter(RightFB1, between(TMIndVertBrk, 15.1, 18), TMHrzBrk >= 10.1, Vel >= 97.1)
    mean(RightFBHighVBVeryHighHBVeryHighVel$ExAVG)
    count(RightFBHighVBVeryHighHBVeryHighVel)


#Very High Velocity Category and Very High VB
RightFBVeryHighVBVeryLowHBVeryHighVel <- filter(RightFB1, TMIndVertBrk >= 18.1, TMHrzBrk <= 3, Vel >= 97.1)
    mean(RightFBVeryHighVBVeryLowHBVeryHighVel$ExAVG)
    count(RightFBVeryHighVBVeryLowHBVeryHighVel)

RightFBVeryHighVBLowHBVeryHighVel <- filter(RightFB1, TMIndVertBrk >= 18.1, between(TMHrzBrk, 3.1, 6), Vel >= 97.1)
    mean(RightFBVeryHighVBLowHBVeryHighVel$ExAVG)
    count(RightFBVeryHighVBLowHBVeryHighVel)

RightFBVeryHighVBAvgHBVeryHighVel <- filter(RightFB1, TMIndVertBrk >= 18.1, between(TMHrzBrk, 6.1, 8), Vel >= 97.1)
    mean(RightFBVeryHighVBAvgHBVeryHighVel$ExAVG)
    count(RightFBVeryHighVBAvgHBVeryHighVel)

RightFBVeryHighVBHighHBVeryHighVel <- filter(RightFB1, TMIndVertBrk >= 18.1, between(TMHrzBrk, 8.1, 10), Vel >= 97.1)
    mean(RightFBVeryHighVBHighHBVeryHighVel$ExAVG)
    count(RightFBVeryHighVBHighHBVeryHighVel)

RightFBVeryHighVBVeryHighHBVeryHighVel <- filter(RightFB1, TMIndVertBrk >= 18.1, TMHrzBrk >= 10.1, Vel >= 97.1)
    mean(RightFBVeryHighVBVeryHighHBVeryHighVel$ExAVG)
    count(RightFBVeryHighVBVeryHighHBVeryHighVel)
```

#Very Low Velo LHP
```{r}
#Very Low Velocity Category and Very Low VB
library(dplyr)
LeftFBVeryLowVBVeryLowHBVeryLowVel <- filter(LeftFB1, TMIndVertBrk <= 10, TMHrzBrk >= -3, Vel <=91)
    mean(LeftFBVeryLowVBVeryLowHBVeryLowVel$ExAVG)
    count(LeftFBVeryLowVBVeryLowHBVeryLowVel)

LeftFBVeryLowVBLowHBVeryLowVel <- filter(LeftFB1, TMIndVertBrk <= 10, between(TMHrzBrk, -6, 3.1), Vel <=91)
    mean(LeftFBVeryLowVBLowHBVeryLowVel$ExAVG)
    count(LeftFBVeryLowVBLowHBVeryLowVel)

LeftFBVeryLowVBAvgHBVeryLowVel <- filter(LeftFB1, TMIndVertBrk <= 10, between(TMHrzBrk, -8, -6.1), Vel <=91)
    mean(LeftFBVeryLowVBAvgHBVeryLowVel$ExAVG)
    count(LeftFBVeryLowVBAvgHBVeryLowVel)

LeftFBVeryLowVBHighHBVeryLowVel <- filter(LeftFB1, TMIndVertBrk <= 10, between(TMHrzBrk, -10, -8.1), Vel <=91)
    mean(LeftFBVeryLowVBHighHBVeryLowVel$ExAVG)
    count(LeftFBVeryLowVBHighHBVeryLowVel)

LeftFBVeryLowVBVeryHighHBVeryLowVel <- filter(LeftFB1, TMIndVertBrk <= 10, TMHrzBrk <= -10.1, Vel <=91)
  mean(LeftFBVeryLowVBVeryHighHBVeryLowVel$ExAVG)
  count(LeftFBVeryLowVBVeryHighHBVeryLowVel)


#Very Low Velocity Category and Low VB
  
LeftFBLowVBVeryLowHBVeryLowVel <- filter(LeftFB1, between(TMIndVertBrk, 10.1, 12), TMHrzBrk >=-3, Vel <=91)
    mean(LeftFBLowVBVeryLowHBVeryLowVel$ExAVG)
    count(LeftFBLowVBVeryLowHBVeryLowVel)
    
LeftFBLowVBLowHBVeryLowVel <- filter(LeftFB1, between(TMIndVertBrk, 10.1, 12), between(TMHrzBrk, -6.0, -3.1), Vel <=91)
    mean(LeftFBLowVBLowHBVeryLowVel$ExAVG)
    count(LeftFBLowVBLowHBVeryLowVel)

LeftFBLowVBAvgHBVeryLowVel <- filter(LeftFB1, between(TMIndVertBrk, 10.1, 12), between(TMHrzBrk, -8.0, -6.1), Vel <=91)
    mean(LeftFBLowVBAvgHBVeryLowVel$ExAVG)
    count(LeftFBLowVBAvgHBVeryLowVel)

LeftFBLowVBHighHBVeryLowVel <- filter(LeftFB1, between(TMIndVertBrk, 10.1, 12), between(TMHrzBrk, -10.0, -8.1), Vel <=91)
    mean(LeftFBLowVBHighHBVeryLowVel$ExAVG)
    count(LeftFBLowVBHighHBVeryLowVel)

LeftFBLowVBVeryHighHBVeryLowVel <- filter(LeftFB1, between(TMIndVertBrk, 10.1, 12), TMHrzBrk <= -10.1, Vel <=91)
    mean(LeftFBLowVBVeryHighHBVeryLowVel$ExAVG)
    count(LeftFBLowVBVeryHighHBVeryLowVel)


#Very Low Velocity Category and Dead VB
LeftFBDeadVBVeryLowHBVeryLowVel <- filter(LeftFB1, between(TMIndVertBrk, 12.1, 15), TMHrzBrk >= -3, Vel <= 91)
    mean(LeftFBDeadVBVeryLowHBVeryLowVel$ExAVG)
    count(LeftFBDeadVBVeryLowHBVeryLowVel)

LeftFBDeadVBLowHBVeryLowVel <- filter(LeftFB1, between(TMIndVertBrk, 12.1, 15), between(TMHrzBrk, -6.0, -3.1), Vel <= 91)
    mean(LeftFBDeadVBLowHBVeryLowVel$ExAVG)
    count(LeftFBDeadVBLowHBVeryLowVel)

LeftFBDeadVBAvgHBVeryLowVel <- filter(LeftFB1, between(TMIndVertBrk, 12.1, 15), between(TMHrzBrk, -8.0, -6.1), Vel <= 91)
    mean(LeftFBDeadVBAvgHBVeryLowVel$ExAVG)
    count(LeftFBDeadVBAvgHBVeryLowVel)
    
LeftFBDeadVBHighHBVeryLowVel <- filter(LeftFB1, between(TMIndVertBrk, 12.1, 15), between(TMHrzBrk, -10, -8.1), Vel <= 91)
    mean(LeftFBDeadVBHighHBVeryLowVel$ExAVG)
    count(LeftFBDeadVBHighHBVeryLowVel)
    
LeftFBDeadVBVeryHighHBVeryLowVel <- filter(LeftFB1, between(TMIndVertBrk, 12.1, 15), TMHrzBrk <= -10.1, Vel <= 91)
    mean(LeftFBDeadVBVeryHighHBVeryLowVel$ExAVG)
    count(LeftFBDeadVBVeryHighHBVeryLowVel)


#Very Low Velocity Category and High VB
LeftFBHighVBVeryLowHBVeryLowVel <- filter(LeftFB1, between(TMIndVertBrk, 15.1, 18), TMHrzBrk >=-3, Vel <= 91)
    mean(LeftFBHighVBVeryLowHBVeryLowVel$ExAVG)
    count(LeftFBHighVBVeryLowHBVeryLowVel)

LeftFBHighVBLowHBVeryLowVel <- filter(LeftFB1, between(TMIndVertBrk, 15.1, 18), between(TMHrzBrk, -6.0, -3.1), Vel <= 91)
    mean(LeftFBHighVBLowHBVeryLowVel$ExAVG)
    count(LeftFBHighVBLowHBVeryLowVel)

LeftFBHighVBAvgHBVeryLowVel <- filter(LeftFB1, between(TMIndVertBrk, 15.1, 18), between(TMHrzBrk, -8.0, -6.1), Vel <= 91)
    mean(LeftFBHighVBAvgHBVeryLowVel$ExAVG)
    count(LeftFBHighVBAvgHBVeryLowVel)
    
LeftFBHighVBHighHBVeryLowVel <- filter(LeftFB1, between(TMIndVertBrk, 15.1, 18), between(TMHrzBrk, -10.0, -8.1), Vel <= 91)
    mean(LeftFBHighVBHighHBVeryLowVel$ExAVG)
    count(LeftFBHighVBHighHBVeryLowVel)
    
LeftFBHighVBVeryHighHBVeryLowVel <- filter(LeftFB1, between(TMIndVertBrk, 15.1, 18), TMHrzBrk <= -10.1, Vel <= 91)
    mean(LeftFBHighVBVeryHighHBVeryLowVel$ExAVG)
    count(LeftFBHighVBVeryHighHBVeryLowVel)

#Very Low Velocity Category and Very High VB
LeftFBVeryHighVBVeryLowHBVeryLowVel <- filter(LeftFB1, TMIndVertBrk >= 18.1, TMHrzBrk >= -3,Vel <= 91)
    mean(LeftFBVeryHighVBVeryLowHBVeryLowVel$ExAVG)
    count(LeftFBVeryHighVBVeryLowHBVeryLowVel)

LeftFBVeryHighVBLowHBVeryLowVel <- filter(LeftFB1, TMIndVertBrk >= 18.1, between(TMHrzBrk, -6.0, -3.1),Vel <= 91)
    mean(LeftFBVeryHighVBLowHBVeryLowVel$ExAVG)
    count(LeftFBVeryHighVBLowHBVeryLowVel)

LeftFBVeryHighVBAvgHBVeryLowVel <- filter(LeftFB1, TMIndVertBrk >= 18.1, between(TMHrzBrk, -8.0, -6.1),Vel <= 91)
    mean(LeftFBVeryHighVBAvgHBVeryLowVel$ExAVG)
    count(LeftFBVeryHighVBAvgHBVeryLowVel)
    
LeftFBVeryHighVBHighHBVeryLowVel <- filter(LeftFB1, TMIndVertBrk >= 18.1, between(TMHrzBrk, -10.0, -8.1),Vel <= 91)
    mean(LeftFBVeryHighVBHighHBVeryLowVel$ExAVG)
    count(LeftFBVeryHighVBHighHBVeryLowVel)
    
LeftFBVeryHighVBVeryHighHBVeryLowVel <- filter(LeftFB1, TMIndVertBrk >= 18.1, TMHrzBrk <= -10.1,Vel <= 91)
    mean(LeftFBVeryHighVBVeryHighHBVeryLowVel$ExAVG)
    count(LeftFBVeryHighVBVeryHighHBVeryLowVel)
```

#Low Velo LHP FB
```{r}
#Low Velocity Category and Very Low VB
LeftFBVeryLowVBVeryLowHBLowVel <- filter(LeftFB1, TMIndVertBrk <= 10, TMHrzBrk >= -3, between(Vel, 91.1, 93))
    mean(LeftFBVeryLowVBVeryLowHBLowVel$ExAVG)
    count(LeftFBVeryLowVBVeryLowHBLowVel)
    
LeftFBVeryLowVBLowHBLowVel <- filter(LeftFB1, TMIndVertBrk <= 10, between(TMHrzBrk, -6.0, -3.1), between(Vel, 91.1, 93))
    mean(LeftFBVeryLowVBLowHBLowVel$ExAVG)
    count(LeftFBVeryLowVBLowHBLowVel)
    
LeftFBVeryLowVBAvgHBLowVel <- filter(LeftFB1, TMIndVertBrk <= 10, between(TMHrzBrk,-8.0, -6.1), between(Vel, 91.1, 93))
    mean(LeftFBVeryLowVBAvgHBLowVel$ExAVG)
    count(LeftFBVeryLowVBAvgHBLowVel)
    
LeftFBVeryLowVBHighHBLowVel <- filter(LeftFB1, TMIndVertBrk <= 10, between(TMHrzBrk, -10.0, -8.1), between(Vel, 91.1, 93))
    mean(LeftFBVeryLowVBHighHBLowVel$ExAVG)
    count(LeftFBVeryLowVBHighHBLowVel)
    
LeftFBVeryLowVBVeryHighHBLowVel <- filter(LeftFB1, TMIndVertBrk <= 10, TMHrzBrk <= -10.1, between(Vel, 91.1, 93))
    mean(LeftFBVeryLowVBVeryHighHBLowVel$ExAVG)
    count(LeftFBVeryLowVBVeryHighHBLowVel)

#Low Velocity Category and Low VB
LeftFBLowVBVeryLowHBLowVel <- filter(LeftFB1, between(TMIndVertBrk, 10.1, 12), TMHrzBrk >= -3, between(Vel, 91.3, 93))
    mean(LeftFBLowVBVeryLowHBLowVel$ExAVG)
    count(LeftFBLowVBVeryLowHBLowVel)
    
LeftFBLowVBLowHBLowVel <- filter(LeftFB1, between(TMIndVertBrk, 10.1, 12), between(TMHrzBrk, -6.0, -3.1), between(Vel, 91.1, 93))
    mean(LeftFBLowVBLowHBLowVel$ExAVG)
    count(LeftFBLowVBLowHBLowVel)
    
LeftFBLowVBAvgHBLowVel <- filter(LeftFB1, between(TMIndVertBrk, 10.1, 12), between(TMHrzBrk, -8.0, -6.1), between(Vel, 91.1, 93))
    mean(LeftFBLowVBAvgHBLowVel$ExAVG)
    count(LeftFBLowVBAvgHBLowVel)

LeftFBLowVBHighHBLowVel <- filter(LeftFB1, between(TMIndVertBrk, 10.1, 12), between(TMHrzBrk, -10.0, -8.1), between(Vel, 91.1, 93))
    mean(LeftFBLowVBHighHBLowVel$ExAVG)
    count(LeftFBLowVBHighHBLowVel)

LeftFBLowVBVeryHighHBLowVel <- filter(LeftFB1, between(TMIndVertBrk, 10.1, 12), TMHrzBrk <= -10.1, between(Vel, 91.1, 93))
    mean(LeftFBLowVBVeryHighHBLowVel$ExAVG)
    count(LeftFBLowVBVeryHighHBLowVel)

#Low Velocity Category and Dead VB
LeftFBDeadVBVeryLowHBLowVel <- filter(LeftFB1, between(TMIndVertBrk, 12.1, 15), TMHrzBrk >= -3, between(Vel, 91.3, 93))
    mean(LeftFBDeadVBVeryLowHBLowVel$ExAVG)
    count(LeftFBDeadVBVeryLowHBLowVel)

LeftFBDeadVBLowHBLowVel <- filter(LeftFB1, between(TMIndVertBrk, 12.1, 15), between(TMHrzBrk, -6.0, -3.1), between(Vel, 91.1, 93))
    mean(LeftFBDeadVBLowHBLowVel$ExAVG)
    count(LeftFBDeadVBLowHBLowVel)

LeftFBDeadVBAvgHBLowVel <- filter(LeftFB1, between(TMIndVertBrk, 12.1, 15), between(TMHrzBrk, -8.0, -6.1), between(Vel, 91.1, 93))
    mean(LeftFBDeadVBAvgHBLowVel$ExAVG)
    count(LeftFBDeadVBAvgHBLowVel)

LeftFBDeadVBHighHBLowVel <- filter(LeftFB1, between(TMIndVertBrk, 12.1, 15), between(TMHrzBrk, -10.0, -8.1), between(Vel, 91.1, 93))
    mean(LeftFBDeadVBHighHBLowVel$ExAVG)
    count(LeftFBDeadVBHighHBLowVel)

LeftFBDeadVBVeryHighHBLowVel <- filter(LeftFB1, between(TMIndVertBrk, 12.1, 15), TMHrzBrk <= -10.1, between(Vel, 91.1, 93))
    mean(LeftFBDeadVBVeryHighHBLowVel$ExAVG)
    count(LeftFBDeadVBVeryHighHBLowVel)

#Low Velocity Category and High VB
LeftFBHighVBVeryLowHBLowVel <- filter(LeftFB1, between(TMIndVertBrk, 15.1, 18), TMHrzBrk >= -3, between(Vel, 91.3, 93))
    mean(LeftFBHighVBVeryLowHBLowVel$ExAVG)
    count(LeftFBHighVBVeryLowHBLowVel)

LeftFBHighVBLowHBLowVel <- filter(LeftFB1, between(TMIndVertBrk, 15.1, 18), between(TMHrzBrk, -6.0, -3.1), between(Vel, 91.1, 93))
    mean(LeftFBHighVBLowHBLowVel$ExAVG)
    count(LeftFBHighVBLowHBLowVel)

LeftFBHighVBAvgHBLowVel <- filter(LeftFB1, between(TMIndVertBrk, 15.1, 18), between(TMHrzBrk, -8.0, -6.1), between(Vel, 91.1, 93))
    mean(LeftFBHighVBAvgHBLowVel$ExAVG)
    count(LeftFBHighVBAvgHBLowVel)

LeftFBHighVBHighHBLowVel <- filter(LeftFB1, between(TMIndVertBrk, 15.1, 18), between(TMHrzBrk, -10.0, -8.1), between(Vel, 91.1, 93))
    mean(LeftFBHighVBHighHBLowVel$ExAVG)
    count(LeftFBHighVBHighHBLowVel)

LeftFBHighVBVeryHighHBLowVel <- filter(LeftFB1, between(TMIndVertBrk, 15.1, 18), TMHrzBrk <= -10.1, between(Vel, 91.1, 93))
    mean(LeftFBHighVBVeryHighHBLowVel$ExAVG)
    count(LeftFBHighVBVeryHighHBLowVel)

#Low Velocity Category and Very High VB
LeftFBVeryHighVBVeryLowHBLowVel <- filter(LeftFB1, TMIndVertBrk >= 18.1, TMHrzBrk >= -3, between(Vel, 91.1, 93))
    mean(LeftFBVeryHighVBVeryLowHBLowVel$ExAVG)
    count(LeftFBVeryHighVBVeryLowHBLowVel)

LeftFBVeryHighVBLowHBLowVel <- filter(LeftFB1, TMIndVertBrk >= 18.1, between(TMHrzBrk, -6.0, -3.1), between(Vel, 91.1, 93))
    mean(LeftFBVeryHighVBLowHBLowVel$ExAVG)
    count(LeftFBVeryHighVBLowHBLowVel)

LeftFBVeryHighVBAvgHBLowVel <- filter(LeftFB1, TMIndVertBrk >= 18.1, between(TMHrzBrk, -8.0, -6.1), between(Vel, 91.1, 93))
    mean(LeftFBVeryHighVBAvgHBLowVel$ExAVG)
    count(LeftFBVeryHighVBAvgHBLowVel)
    
LeftFBVeryHighVBHighHBLowVel <- filter(LeftFB1, TMIndVertBrk >= 18.1, between(TMHrzBrk, -10.0, -8.1), between(Vel, 91.1, 93))
    mean(LeftFBVeryHighVBHighHBLowVel$ExAVG)
    count(LeftFBVeryHighVBHighHBLowVel)

LeftFBVeryHighVBVeryHighHBLowVel <- filter(LeftFB1, TMIndVertBrk >= 18.1, TMHrzBrk <= -10.1, between(Vel, 91.1, 93))
    mean(LeftFBVeryHighVBVeryHighHBLowVel$ExAVG)
    count(LeftFBVeryHighVBVeryHighHBLowVel)
```

#Average Velo LHP FB
```{r}
#Avg Velocity Category and Very Low VB
LeftFBVeryLowVBVeryLowHBAvgVel <- filter(LeftFB1, TMIndVertBrk <= 10, TMHrzBrk >= -3, between(Vel, 93.1, 95))
    mean(LeftFBVeryLowVBVeryLowHBAvgVel$ExAVG)
    count(LeftFBVeryLowVBVeryLowHBAvgVel)

LeftFBVeryLowVBLowHBAvgVel <- filter(LeftFB1, TMIndVertBrk <= 10, between(TMHrzBrk, -6.0, -3.1), between(Vel, 93.1, 95))
    mean(LeftFBVeryLowVBLowHBAvgVel$ExAVG)
    count(LeftFBVeryLowVBLowHBAvgVel)

LeftFBVeryLowVBAvgHBAvgVel <- filter(LeftFB1, TMIndVertBrk <= 10, between(TMHrzBrk, -8.0, -6.1), between(Vel, 93.1, 95))
    mean(LeftFBVeryLowVBAvgHBAvgVel$ExAVG)
    count(LeftFBVeryLowVBAvgHBAvgVel)

LeftFBVeryLowVBHighHBAvgVel <- filter(LeftFB1, TMIndVertBrk <= 10, between(TMHrzBrk, -10.0, -8.1), between(Vel, 93.1, 95))
    mean(LeftFBVeryLowVBHighHBAvgVel$ExAVG)
    count(LeftFBVeryLowVBHighHBAvgVel)

LeftFBVeryLowVBVeryHighHBAvgVel <- filter(LeftFB1, TMIndVertBrk <= 10, TMHrzBrk <= -10.1, between(Vel, 93.1, 95))
    mean(LeftFBVeryLowVBVeryHighHBAvgVel$ExAVG)
    count(LeftFBVeryLowVBVeryHighHBAvgVel)


#Avg Velocity Category and Low VB
LeftFBLowVBVeryLowHBAvgVel <- filter(LeftFB1, between(TMIndVertBrk, 10.1, 12), TMHrzBrk >= -3, between(Vel, 93.1, 95))
    mean(LeftFBLowVBVeryLowHBAvgVel$ExAVG)
    count(LeftFBLowVBVeryLowHBAvgVel)

LeftFBLowVBLowHBAvgVel <- filter(LeftFB1, between(TMIndVertBrk, 10.1, 12), between(TMHrzBrk, -6.0, -3.1), between(Vel, 93.1, 95))
    mean(LeftFBLowVBLowHBAvgVel$ExAVG)
    count(LeftFBLowVBLowHBAvgVel)

LeftFBLowVBAvgHBAvgVel <- filter(LeftFB1, between(TMIndVertBrk, 10.1, 12), between(TMHrzBrk, -8.0, -6.1), between(Vel, 93.1, 95))
    mean(LeftFBLowVBAvgHBAvgVel$ExAVG)
    count(LeftFBLowVBAvgHBAvgVel)
    
LeftFBLowVBHighHBAvgVel <- filter(LeftFB1, between(TMIndVertBrk, 10.1, 12), between(TMHrzBrk, -10.0, -8.1), between(Vel, 93.1, 95))
    mean(LeftFBLowVBHighHBAvgVel$ExAVG)
    count(LeftFBLowVBHighHBAvgVel)

LeftFBLowVBVeryHighHBAvgVel <- filter(LeftFB1, between(TMIndVertBrk, 10.1, 12), TMHrzBrk <= -10.1, between(Vel, 93.1, 95))
    mean(LeftFBLowVBVeryHighHBAvgVel$ExAVG)
    count(LeftFBLowVBVeryHighHBAvgVel)

#Avg Velocity Category and Dead VB
LeftFBDeadVBVeryLowHBAvgVel <- filter(LeftFB1, between(TMIndVertBrk, 12.1, 15), TMHrzBrk >= -3, between(Vel, 93.1, 95))
    mean(LeftFBDeadVBVeryLowHBAvgVel$ExAVG)
    count(LeftFBDeadVBVeryLowHBAvgVel)

LeftFBDeadVBLowHBAvgVel <- filter(LeftFB1, between(TMIndVertBrk, 12.1, 15), between(TMHrzBrk, -6.0, -3.1), between(Vel, 93.1, 95))
    mean(LeftFBDeadVBLowHBAvgVel$ExAVG)
    count(LeftFBDeadVBLowHBAvgVel)

LeftFBDeadVBAvgHBAvgVel <- filter(LeftFB1, between(TMIndVertBrk, 12.1, 15), between(TMHrzBrk, -8.0, -6.1), between(Vel, 93.1, 95))
    mean(LeftFBDeadVBAvgHBAvgVel$ExAVG)
    count(LeftFBDeadVBAvgHBAvgVel)

LeftFBDeadVBHighHBAvgVel <- filter(LeftFB1, between(TMIndVertBrk, 12.1, 15), between(TMHrzBrk, -10.0, -8.1), between(Vel, 93.1, 95))
    mean(LeftFBDeadVBHighHBAvgVel$ExAVG)
    count(LeftFBDeadVBHighHBAvgVel)

LeftFBDeadVBVeryHighHBAvgVel <- filter(LeftFB1, between(TMIndVertBrk, 12.1, 15), TMHrzBrk <= -10.1, between(Vel, 93.1, 95))
    mean(LeftFBDeadVBVeryHighHBAvgVel$ExAVG)
    count(LeftFBDeadVBVeryHighHBAvgVel)

#Avg Velocity Category and High VB
LeftFBHighVBVeryLowHBAvgVel <- filter(LeftFB1, between(TMIndVertBrk, 15.1, 18), TMHrzBrk >= -3, between(Vel, 93.1, 95))
    mean(LeftFBHighVBVeryLowHBAvgVel$ExAVG)
    count(LeftFBHighVBVeryLowHBAvgVel)

LeftFBHighVBLowHBAvgVel <- filter(LeftFB1, between(TMIndVertBrk, 15.1, 18), between(TMHrzBrk, -6.0, -3.1), between(Vel, 93.1, 95))
    mean(LeftFBHighVBLowHBAvgVel$ExAVG)
    count(LeftFBHighVBLowHBAvgVel)

LeftFBHighVBAvgHBAvgVel <- filter(LeftFB1, between(TMIndVertBrk, 15.1, 18), between(TMHrzBrk, -8.0, -6.1), between(Vel, 93.1, 95))
    mean(LeftFBHighVBAvgHBAvgVel$ExAVG)
    count(LeftFBHighVBAvgHBAvgVel)

LeftFBHighVBHighHBAvgVel <- filter(LeftFB1, between(TMIndVertBrk, 15.1, 18), between(TMHrzBrk, -10.0, -8.1), between(Vel, 93.1, 95))
    mean(LeftFBHighVBHighHBAvgVel$ExAVG)
    count(LeftFBHighVBHighHBAvgVel)

LeftFBHighVBVeryHighHBAvgVel <- filter(LeftFB1, between(TMIndVertBrk, 15.1, 18), TMHrzBrk <= -10.1, between(Vel, 93.1, 95))
    mean(LeftFBHighVBVeryHighHBAvgVel$ExAVG)
    count(LeftFBHighVBVeryHighHBAvgVel)

#Avg Velocity Category and Very High VB
LeftFBVeryHighVBVeryLowHBAvgVel <- filter(LeftFB1, TMIndVertBrk >= 18.1, TMHrzBrk >= -3, between(Vel, 93.1, 95))
    mean(LeftFBVeryHighVBVeryLowHBAvgVel$ExAVG)
    count(LeftFBVeryHighVBVeryLowHBAvgVel)

LeftFBVeryHighVBLowHBAvgVel <- filter(LeftFB1, TMIndVertBrk >= 18.1, between(TMHrzBrk, -6.0, -3.1), between(Vel, 93.1, 95))
    mean(LeftFBVeryHighVBLowHBAvgVel$ExAVG)
    count(LeftFBVeryHighVBLowHBAvgVel)

LeftFBVeryHighVBAvgHBAvgVel <- filter(LeftFB1, TMIndVertBrk >= 18.1, between(TMHrzBrk, -8.0, -6.1), between(Vel, 93.1, 95))
    mean(LeftFBVeryHighVBAvgHBAvgVel$ExAVG)
    count(LeftFBVeryHighVBAvgHBAvgVel)

LeftFBVeryHighVBHighHBAvgVel <- filter(LeftFB1, TMIndVertBrk >= 18.1, between(TMHrzBrk, -10.0, -8.1), between(Vel, 93.1, 95))
    mean(LeftFBVeryHighVBHighHBAvgVel$ExAVG)
    count(LeftFBVeryHighVBHighHBAvgVel)

LeftFBVeryHighVBVeryHighHBAvgVel <- filter(LeftFB1, TMIndVertBrk >= 18.1, TMHrzBrk <= -10.1, between(Vel, 93.1, 95))
    mean(LeftFBVeryHighVBVeryHighHBAvgVel$ExAVG)
    count(LeftFBVeryHighVBVeryHighHBAvgVel)
```

#High Velocity LHP
```{r}
#High Velocity Category and Very Low VB
LeftFBVeryLowVBVeryLowHBHighVel <- filter(LeftFB1, TMIndVertBrk <= 10, TMHrzBrk >= -3, between(Vel, 95.1, 97))
  mean(LeftFBVeryLowVBVeryLowHBHighVel$ExAVG)
  count(LeftFBVeryLowVBVeryLowHBHighVel)

LeftFBVeryLowVBLowHBHighVel <- filter(LeftFB1, TMIndVertBrk <= 10, between(TMHrzBrk, -6.0, -3.1), between(Vel, 95.1, 97))
  mean(LeftFBVeryLowVBLowHBHighVel$ExAVG)
  count(LeftFBVeryLowVBLowHBHighVel)

LeftFBVeryLowVBAvgHBHighVel <- filter(LeftFB1, TMIndVertBrk <= 10, between(TMHrzBrk,-8.0, -6.1), between(Vel, 95.1, 97))
    mean(LeftFBVeryLowVBAvgHBHighVel$ExAVG)
    count(LeftFBVeryLowVBAvgHBHighVel)

LeftFBVeryLowVBHighHBHighVel <- filter(LeftFB1, TMIndVertBrk <= 10, between(TMHrzBrk, -10.0, -8.1), between(Vel, 95.1, 97))
    mean(LeftFBVeryLowVBHighHBHighVel$ExAVG)
    count(LeftFBVeryLowVBHighHBHighVel)

LeftFBVeryLowVBVeryHighHBHighVel <- filter(LeftFB1, TMIndVertBrk <= 10, TMHrzBrk <= -10.1, between(Vel, 95.1, 97))
    mean(LeftFBVeryLowVBVeryHighHBHighVel$ExAVG)
    count(LeftFBVeryLowVBVeryHighHBHighVel)

#High Velocity Category and Low VB
LeftFBLowVBVeryLowHBHighVel <- filter(LeftFB1, between(TMIndVertBrk, 10.1, 12), TMHrzBrk >= -3, between(Vel, 95.1, 97))
    mean(LeftFBLowVBVeryLowHBHighVel$ExAVG)
    count(LeftFBLowVBVeryLowHBHighVel)

LeftFBLowVBLowHBHighVel <- filter(LeftFB1, between(TMIndVertBrk, 10.1, 12), between(TMHrzBrk, -6.0, -3.1), between(Vel, 95.1, 97))
    mean(LeftFBLowVBLowHBHighVel$ExAVG)
    count(LeftFBLowVBLowHBHighVel)
    
LeftFBLowVBAvgHBHighVel <- filter(LeftFB1, between(TMIndVertBrk, 10.1, 12), between(TMHrzBrk, -8.0, -6.1), between(Vel, 95.1, 97))
    mean(LeftFBLowVBAvgHBHighVel$ExAVG)
    count(LeftFBLowVBAvgHBHighVel)

LeftFBLowVBHighHBHighVel <- filter(LeftFB1, between(TMIndVertBrk, 10.1, 12), between(TMHrzBrk, -10.0, -8.1), between(Vel, 95.1, 97))
    mean(LeftFBLowVBHighHBHighVel$ExAVG)
    count(LeftFBLowVBHighHBHighVel)

LeftFBLowVBVeryHighHBHighVel <- filter(LeftFB1, between(TMIndVertBrk, 10.1, 12), TMHrzBrk <= -10.1, between(Vel, 95.1, 97))
    mean(LeftFBLowVBVeryHighHBHighVel$ExAVG)
    count(LeftFBLowVBVeryHighHBHighVel)

#High Velocity Category and Dead VB
LeftFBDeadVBVeryLowHBHighVel <- filter(LeftFB1, between(TMIndVertBrk, 12.1, 15), TMHrzBrk >= -3, between(Vel, 95.1, 97))
    mean(LeftFBDeadVBVeryLowHBHighVel$ExAVG)
    count(LeftFBDeadVBVeryLowHBHighVel)

LeftFBDeadVBLowHBHighVel <- filter(LeftFB1, between(TMIndVertBrk, 12.1, 15), between(TMHrzBrk, -6.0, -3.1), between(Vel, 95.1, 97))
    mean(LeftFBDeadVBLowHBHighVel$ExAVG)
    count(LeftFBDeadVBLowHBHighVel)

LeftFBDeadVBAvgHBHighVel <- filter(LeftFB1, between(TMIndVertBrk, 12.1, 15), between(TMHrzBrk, -8.0, -6.1), between(Vel, 95.1, 97))
    mean(LeftFBDeadVBAvgHBHighVel$ExAVG)
    count(LeftFBDeadVBAvgHBHighVel)

LeftFBDeadVBHighHBHighVel <- filter(LeftFB1, between(TMIndVertBrk, 12.1, 15), between(TMHrzBrk, -10.0, -8.1), between(Vel, 95.1, 97))
    mean(LeftFBDeadVBHighHBHighVel$ExAVG)
    count(LeftFBDeadVBHighHBHighVel)

LeftFBDeadVBVeryHighHBHighVel <- filter(LeftFB1, between(TMIndVertBrk, 12.1, 15), TMHrzBrk <= -10.1, between(Vel, 95.1, 97))
    mean(LeftFBDeadVBVeryHighHBHighVel$ExAVG)
    count(LeftFBDeadVBVeryHighHBHighVel)

#High Velocity Category and High VB
LeftFBHighVBVeryLowHBHighVel <- filter(LeftFB1, between(TMIndVertBrk, 15.1, 18), TMHrzBrk >= -3, between(Vel, 95.1, 97))
    mean(LeftFBHighVBVeryLowHBHighVel$ExAVG)
    count(LeftFBHighVBVeryLowHBHighVel)

LeftFBHighVBLowHBHighVel <- filter(LeftFB1, between(TMIndVertBrk, 15.1, 18), between(TMHrzBrk, -6.0, -3.1), between(Vel, 95.1, 97))
    mean(LeftFBHighVBLowHBHighVel$ExAVG)
    count(LeftFBHighVBLowHBHighVel)

LeftFBHighVBAvgHBHighVel <- filter(LeftFB1, between(TMIndVertBrk, 15.1, 18), between(TMHrzBrk, -8.0, -6.1), between(Vel, 95.1, 97))
    mean(LeftFBHighVBAvgHBHighVel$ExAVG)
    count(LeftFBHighVBAvgHBHighVel)

LeftFBHighVBHighHBHighVel <- filter(LeftFB1, between(TMIndVertBrk, 15.1, 18), between(TMHrzBrk, -10.0, -8.1), between(Vel, 95.1, 97))
    mean(LeftFBHighVBHighHBHighVel$ExAVG) 
    count(LeftFBHighVBHighHBHighVel)

LeftFBHighVBVeryHighHBHighVel <- filter(LeftFB1, between(TMIndVertBrk, 15.1, 18), TMHrzBrk <= -10.1, between(Vel, 95.1, 97))
    mean(LeftFBHighVBVeryHighHBHighVel$ExAVG)
    count(LeftFBHighVBVeryHighHBHighVel)

#High Velocity Category and Very High VB
LeftFBVeryHighVBVeryLowHBHighVel <- filter(LeftFB1, TMIndVertBrk >= 18.1, TMHrzBrk >= -3, between(Vel, 95.1, 97))
    mean(LeftFBVeryHighVBVeryLowHBHighVel$ExAVG)
    count(LeftFBVeryHighVBVeryLowHBHighVel)

LeftFBVeryHighVBLowHBHighVel <- filter(LeftFB1, TMIndVertBrk >= 18.1, between(TMHrzBrk, -6.0, -3.1), between(Vel, 95.1, 97))
    mean(LeftFBVeryHighVBLowHBHighVel$ExAVG)
    count(LeftFBVeryHighVBLowHBHighVel)

LeftFBVeryHighVBAvgHBHighVel <- filter(LeftFB1, TMIndVertBrk >= 18.1, between(TMHrzBrk, -8.0, -6.1), between(Vel, 95.1, 97))
    mean(LeftFBVeryHighVBAvgHBHighVel$ExAVG)
    count(LeftFBVeryHighVBAvgHBHighVel)

LeftFBVeryHighVBHighHBHighVel <- filter(LeftFB1, TMIndVertBrk >= 18.1, between(TMHrzBrk, -10.0, -8.1), between(Vel, 95.1, 97))
    mean(LeftFBVeryHighVBHighHBHighVel$ExAVG)
    count(LeftFBVeryHighVBHighHBHighVel)

LeftFBVeryHighVBVeryHighHBHighVel <- filter(LeftFB1, TMIndVertBrk >= 18.1, TMHrzBrk <= -10.1, between(Vel, 95.1, 97))
    mean(LeftFBVeryHighVBVeryHighHBHighVel$ExAVG)
    count(LeftFBVeryHighVBVeryHighHBHighVel)
```



